The Impact of Educational Expenses of New Coders

### 2021-04-16 outputs/paper/paper.Rmd
Edit regression model table

### Print correlation coefficient
tblCorr <-
  dfNewCoders %>%
  as.matrix() %>%
  apaCorr() %>%
  data.frame() %>%
  kable(caption = "Correlation matrix for variables",
        booktabs = TRUE,
        col.names = c("1", "2", "3", "4", "5", "6","7","8")) %>%
  footnote(general = "* p < 0.05, ** p < 0.01, *** p < 0.001",
             general_title = "")

@@

```{r}
#### Multiple regression analysis ####
summary(fit.lm <- lm(formula = 
                       MoneyForLearning ~ 
                       Gender +
                       CityPopulation +
                       CommuteTime +
                       Income +
                       MonthsProgramming +
                       SchoolDegree, 
                     data = dfNewCoders))
```
```{r}
#### Beta ####
QuantPsyc::lm.beta(fit.lm)
```

@@

```{r}

>>>>

### Print correlation coefficient
tblCorr <-
  dfNewCoders %>%
  as.matrix() %>%
  apaCorr() %>%
  data.frame() %>%
  kable(caption = "Correlation matrix for variables",
        booktabs = TRUE,
        col.names = c("1", "2", "3", "4", "5", "6", "7", "8")) %>%
  footnote(general = "* p < 0.05, ** p < 0.01, *** p < 0.001",
             general_title = "")

@@

```{r, results='asis'}
#### Multiple regression analysis ####
fit.lm <- lm(formula = 
               MoneyForLearning ~ 
               Gender +
               CityPopulation +
               CommuteTime +
               Income +
               MonthsProgramming +
               SchoolDegree, 
               data = dfNewCoders)

# summary(fit.lm)
stargazer::stargazer(fit.lm, 
          title = "Result of regression model", 
          header = FALSE,
          type = "latex")
```

```{r}
#### Beta ####
QuantPsyc::lm.beta(fit.lm)
```

@@

```{r}
# TODO: RMSE
```
